\LARGE \bf Experimental Validation of Reference Spreading by Robotic Manipulation of Unmodeled Objects

### 2023-01-03 QP.tex
a

\text{\textbf{Reference Spreading}}\\
\varphi  \quad \text{Time of impact}\\
\gamma  \quad \text{Impact time-based interpolation variable}\\
T  \quad \text{Duration of interim impact mode}\\
m \quad \text{Intermediate impact mode(0: no RS, 1: Jari, 2: Sven, 3: mixing)}\\\\
\text{\textbf{Sub- and superscripts}}\\
(\cdot)^{a} \quad \text{Ante-impact signal}\\
(\cdot)^{p} \quad \text{Post-impact signal}\\
(\cdot)_{dem} \quad \text{Signals from VR device during recording}\\
(\cdot)_{rec} \;\quad \text{Signals measured from robot or calculated during recording}\\
(\cdot)_{ref} \;\quad \text{Signals determined using RS scheme}\\
(\cdot)_{rep} \;\quad \text{Signals measured from robot or calculated during replay}\\
\end{array}$
\newpage
\section*{Recording}

$\begin{array}{l}
\ddot{q}_{rec} = \min_{\ddot{q}}\left \|  \begin{bmatrix}
\alpha(\ddot{q})\\ 
a(\ddot{q})
\end{bmatrix} - \Lambda^{-1}f_{rec} \right \| + \left \| \ddot{q}_1-\beta_{rec} \right \|\\\\
f_{rec} =2(\Lambda K_{rec})^{\frac{1}{2}} \begin{bmatrix}
\omega_{dem} - \omega_{rec}
\\ 
v_{dem}-v_{rec}
\end{bmatrix} + K_{rec} \begin{bmatrix}
R_{rec}(\log({R_{rec}}^TR_{dem}))^{\vee }\\ 
p_{dem}-p_{rec}
\end{bmatrix}\\\\
\beta_{rec} = 2\sqrt{k_{rec}}\left [ -\dot{q}_{1,rec}  \right ] + k_{rec}\left [ -q_{1,rec}  \right ]

\end{array}$\\
\includegraphics[trim={1cm 23.3cm 5cm 1cm}, clip]{Graphics/qp.pdf}\\
\section*{Reference Extending}
$\begin{array}{l}
REhold(x,t,\varphi) 
% = \begin{bmatrix} x^a(t) & x^p(t) \end{bmatrix} 
= \begin{cases} 
\begin{bmatrix} x(t) & x(\varphi) \end{bmatrix},& \text{if } t\leq \varphi\\
\begin{bmatrix} x(\varphi) & x(t) \end{bmatrix},& \text{if } t> \varphi\\
\end{cases}\\\\\\

REintegrate(x,y,t,\varphi) 
% = \begin{bmatrix} y^a(t) & y^p(t) \end{bmatrix} 
= \begin{cases} 
\begin{bmatrix} x(t) & x(\varphi) \end{bmatrix}+\begin{bmatrix}0 & y(\varphi)(t-\varphi) \end{bmatrix},& \text{if } t\leq \varphi\\
\begin{bmatrix} x(\varphi) & x(t) \end{bmatrix}+\begin{bmatrix}y(\varphi)(t-\varphi) & 0  \end{bmatrix},& \text{if } t> \varphi\\
\end{cases}\\\\

\begin{bmatrix} R_{rec}^a(t) & R_{rec}^p(t) \end{bmatrix} 
= \begin{cases} 
\begin{bmatrix} R_{rec}(t) & R_{rec}(\varphi_{rec})e^{\omega_{rec}(\varphi_{rec})(t-\varphi_{rec})} \end{bmatrix},& \text{if } t\leq  \varphi_{rec}\\
\begin{bmatrix} R_{rec}(\varphi_{rec})e^{\omega_{rec}(\varphi_{rec})(t-\varphi_{rec})} & R_{rec}(t) \end{bmatrix},& \text{if } t> \varphi_{rec}\\
\end{cases}\\

\begin{bmatrix} p_{rec}^a(t) & p_{rec}^p(t) \end{bmatrix} = REintegrate(p_{rec},\dot{q}_{1,rec},t,\varphi_{rec})\\
\begin{bmatrix} q_{1,rec}^a(t) & q_{1,rec}^p(t) \end{bmatrix} = REintegrate(q_{1,rec},\dot{q}_{1,rec},t,\varphi_{rec})\\

\begin{bmatrix} f_{rec}^a(t) & f_{rec}^p(t) \end{bmatrix} = REhold(f_{rec},t,\varphi_{rec})\\
\begin{bmatrix} \beta_{rec}^a(t) & \beta_{rec}^p(t) \end{bmatrix} = REhold(\beta_{rec},t,\varphi_{rec})\\
\begin{bmatrix} v_{rec}^a(t) & v_{rec}^p(t) \end{bmatrix} = REhold(v_{rec},t,\varphi_{rec})\\
\begin{bmatrix} \omega_{rec}^a(t) & \omega_{rec}^p(t) \end{bmatrix} = REhold(\omega_{rec},t,\varphi_{rec})\\
\begin{bmatrix} \dot{q}_{1,rec}^a(t) & \dot{q}_{1,rec}^p(t) \end{bmatrix} = REhold(\dot{q}_{1,rec},t,\varphi_{rec})
\end{array}$

@@

\newpage
\section*{Replaying}
$\begin{array}{l}
\ddot{q}_{rep} = \min_{\ddot{q}}\left \|  \begin{bmatrix}
\alpha(\ddot{q})\\ 
a(\ddot{q})
\end{bmatrix} - \Lambda^{-1}(f_{rep}+f_{rec}) \right \| + \left \|\ddot{q}_1-(\beta_{rep}+\beta_{rec}) \right \|\\\\
f_{rep} =2(\Lambda K_{rep})^{\frac{1}{2}} \begin{bmatrix}
\omega_{rec} - \omega_{rep}
\\ 
v_{rec}-v_{rep}
\end{bmatrix} + K_{rep} \begin{bmatrix}
R_{rep}(\log({R_{rep}}^TR_{rec}))^{\vee }\\ 
p_{rec}-p_{rep}
\end{bmatrix}\\\\
\beta_{rep} = 2\sqrt{k_{rep}}\left [ \dot{q}_{1,rec}-\dot{q}_{1,rep}  \right ] + k_{rep}\left [ q_{1,rec}-q_{1,rep}  \right ]
\end{array}$

\includegraphics[trim={1cm 17.8cm 5cm 6.5cm}, clip]{Graphics/qp.pdf}

>>>>

\text{\textbf{Reference Spreading}}\\
\varphi  \quad \text{Time of impact}\\
\gamma  \quad \text{Normalized time since impact}\\
T  \quad \text{Duration of interim impact mode}\\
m \quad \text{Intermediate impact mode selector (0: no RS, 1: Jari, 2: Sven, 3: mixing)}\\\\
\text{\textbf{Sub- and superscripts}}\\
(\cdot)^{a} \quad \text{Ante-impact signal}\\
(\cdot)^{p} \quad \text{Post-impact signal}\\
(\cdot)_{dem} \quad \text{Signals from VR device during recording}\\
(\cdot)_{rec} \;\quad \text{Signals measured from robot or calculated during recording}\\
(\cdot)_{ref} \;\quad \text{Signals determined using RS scheme}\\
(\cdot)_{rep} \;\quad \text{Signals measured from robot or calculated during replay}\\
\end{array}$
\newpage
\section*{Recording}

$\begin{array}{l}
\ddot{q}_{rec} = \min\limits_{\ddot{q}}\left \|  \begin{bmatrix}
\alpha(\ddot{q})\\ 
a(\ddot{q})
\end{bmatrix} - \Lambda^{-1}f_{rec} \right \| + \left \| \ddot{q}_1-\beta_{rec} \right \|\\\\
f_{rec} =2(\Lambda K_{rec})^{\frac{1}{2}} \begin{bmatrix}
\omega_{dem} - \omega_{rec}
\\ 
v_{dem}-v_{rec}
\end{bmatrix} + K_{rec} \begin{bmatrix}
R_{rec}(\log({R_{rec}}^TR_{dem}))^{\vee }\\ 
p_{dem}-p_{rec}
\end{bmatrix}\\\\
\beta_{rec} = 2\sqrt{k_{rec}}\left [ -\dot{q}_{1,rec}  \right ] + k_{rec}\left [ -q_{1,rec}  \right ]

\end{array}$\\
\includegraphics[trim={1cm 23.3cm 5cm 1cm}, clip]{Graphics/qp.pdf}\\

\section*{Replaying}
$\begin{array}{l}
\ddot{q}_{rep} = \min\limits_{\ddot{q}}\left \|  \begin{bmatrix}
\alpha(\ddot{q})\\ 
a(\ddot{q})
\end{bmatrix} - \Lambda^{-1}(f_{rep}+f_{rec}) \right \| + \left \|\ddot{q}_1-(\beta_{rep}+\beta_{rec}) \right \|\\\\
f_{rep} =2(\Lambda K_{rep})^{\frac{1}{2}} \begin{bmatrix}
\omega_{rec} - \omega_{rep}
\\ 
v_{rec}-v_{rep}
\end{bmatrix} + K_{rep} \begin{bmatrix}
R_{rep}(\log({R_{rep}}^TR_{rec}))^{\vee }\\ 
p_{rec}-p_{rep}
\end{bmatrix}\\\\
\beta_{rep} = 2\sqrt{k_{rep}}\left [ \dot{q}_{1,rec}-\dot{q}_{1,rep}  \right ] + k_{rep}\left [ q_{1,rec}-q_{1,rep}  \right ]
\end{array}$

\includegraphics[trim={1cm 17.8cm 5cm 6.5cm}, clip]{Graphics/qp.pdf}
\\
\section*{Reference Extending}
$\begin{array}{l}
REhold(x,t,\varphi) 
% = \begin{bmatrix} x^a(t) & x^p(t) \end{bmatrix} 
= \begin{cases} 
\begin{bmatrix} x(t) & x(\varphi) \end{bmatrix},& \text{if } t\leq \varphi\\
\begin{bmatrix} x(\varphi) & x(t) \end{bmatrix},& \text{if } t> \varphi\\
\end{cases}\\\\\\

REintergrate(x,y,t,\varphi) 
% = \begin{bmatrix} y^a(t) & y^p(t) \end{bmatrix} 
= \begin{cases} 
\begin{bmatrix} x(t) & x(\varphi) \end{bmatrix}+\begin{bmatrix}0 & y(\varphi)(t-\varphi) \end{bmatrix},& \text{if } t\leq \varphi\\
\begin{bmatrix} x(\varphi) & x(t) \end{bmatrix}+\begin{bmatrix}y(\varphi)(t-\varphi) & 0  \end{bmatrix},& \text{if } t> \varphi\\
\end{cases}\\\\

REintergrateRot(R,\omega,t,\varphi) 
% = \begin{bmatrix} y^a(t) & y^p(t) \end{bmatrix} 
= \begin{cases} 
\begin{bmatrix} R(t) & R(\varphi)e^{\omega(\varphi)(t-\varphi)} \end{bmatrix},& \text{if } t\leq  \varphi\\
\begin{bmatrix} R(\varphi)e^{\omega(\varphi)(t-\varphi)} & R(t) \end{bmatrix},& \text{if } t> \varphi\\
\end{cases}\\
\\

\begin{bmatrix} R_{rec}^a(t) & R_{rec}^p(t) \end{bmatrix} 
= REintergrateRot(R_{rec},\omega_{rec},t,\varphi_{rec}) \\
\\

\begin{bmatrix} 
p_{rec}^a(t) & p_{rec}^p(t) \\
 q_{1,rec}^a(t) & q_{1,rec}^p(t)
\end{bmatrix} = REintergrate(
\begin{bmatrix} 
p_{rec}\\
 q_{1,rec}
\end{bmatrix} 
,\begin{bmatrix} 
v_{rec}\\
 \dot{q}_{1,rec}
\end{bmatrix} 
,t,\varphi_{rec})\\
\\

\begin{bmatrix} 
\omega_{rec}^a(t)&\omega_{rec}^p(t)\\
v_{rec}^a(t)&v_{rec}^p(t)\\
 \dot{q}_{1,rec}^a(t)&\dot{q}_{1,rec}^p(t)\\
 f_{rec}^a(t)&f_rec^p(t)\\
 \beta_{rec}^a(t)&\beta_{rec}^p(t)
\end{bmatrix} = REhold(
\begin{bmatrix} 
\omega_{rec}\\
v_{rec}\\
 \dot{q}_{1,rec}\\
 f_{ref}\\
 \beta_{rec}
\end{bmatrix} 
,t,\varphi_{rec})\\
\end{array}$

@@

\newpage
